Prospective testing for the prevalence or transience of a shock effect before it occurs

### 2021-12-05 prevalence_testing/postshocktest2021draft.tex
new codes for functions and data analysis and some addition to manuscript

\begin{corollary}
\label{coro1}Let $(w_2, \ldots, w_{n+1})$ be weights such that $w_i \in [0,1]$ and $\sum_{i=2}^{n+1} w_i=1$. Define
\begin{align*}
  \mc{I}_n = \{i = \in 2,\ldots, n+1\colon 0< w_i < 1\}.
\end{align*}
Suppose that  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$ as $n \to \infty$, and $w_i b_n\leq K$ for $i\in \mc{I}_n$ and some $K>0$, where $b_n \geq 1$ and $b_n \to \infty$ as $n\to \infty$. Assume for $i \in \mc{I}_n$,  $p_i$ are pairwise independent $p$-values  with 
\begin{align*}
  \sum_{i\in \mc{I}_n}\P(p_i \leq \alpha) = \sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_{1},
\end{align*}
where $\kappa_i =  \P(p_i \leq \alpha)\in [0,1]$ for $i \in \mc{I}_n$, $\alpha$ is the significance level, $\kappa_1 = \P(p_1 \leq \alpha)$, and  $p_1$ is the p-value of the time series of interest. If $\P(p_1 \leq \alpha) \neq 0.5$,
\begin{align*}
  \E \bigg\{\left|I\left\{ \sum_{i\in \mc{I}_n} w_i I(p_i \leq  \alpha) \geq 0.5\right\}
  - I( p_1 \leq  \alpha) \right|\bigg\}
  \to  \begin{cases}
    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
  \end{cases}
\end{align*}
\end{corollary}

@@

@@

>>>>

\begin{corollary}
\label{coro1}Let $(w_2, \ldots, w_{n+1})$ be weights such that $w_i \in [0,1]$ and $\sum_{i=2}^{n+1} w_i=1$. Define
\begin{align*}
  \mc{I}_n = \{i =  2,\ldots, n+1\colon 0< w_i < 1\}.
\end{align*}
Suppose that  $\mc{I}_n$  is non-empty, $|\mc{I}_n| \to \infty$ as $n \to \infty$, and $w_i b_n\leq K$ for $i\in \mc{I}_n$ and some $K>0$, where $b_n \geq 1$ and $b_n \to \infty$ as $n\to \infty$. Assume for $i \in \mc{I}_n$,  $p_i$ are pairwise independent $p$-values  with 
\begin{align*}
  \sum_{i\in \mc{I}_n}\P(p_i \leq \alpha) = \sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_{1},
\end{align*}
where $\kappa_i =  \P(p_i \leq \alpha)\in [0,1]$ for $i \in \mc{I}_n$, $\alpha$ is the significance level, $\kappa_1 = \P(p_1 \leq \alpha)$, and  $p_1$ is the p-value of the time series of interest. If $\P(p_1 \leq \alpha) \neq 0.5$,
\begin{align*}
  \E \bigg\{\left|I\left\{ \sum_{i\in \mc{I}_n} w_i I(p_i \leq  \alpha) \geq 0.5\right\}
  - I( p_1 \leq  \alpha) \right|\bigg\}
  \to  \begin{cases}
    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
  \end{cases}
\end{align*}
\end{corollary}

@@

Note that asymptotic approximation for the misclassification error does not work when the weight is concentrated, i.e., $\mc{I}_n$ is finite even if $n\to \infty$, where $\mc{I}_n = \{i =  2,\ldots, n+1\colon 0< w_i < 1\}$. The intuition is that  it is impossible to find a weight to constrain the random behavior of the Bernoulli random variables $I(p_i\leq \alpha)$ for $i \in \mc{I}_n$ such that the weak law of large number can apply.  Nevertheless, in this case, if $\kappa_i = \P(p_i\leq \alpha)$ for $i\in \mc{I}_n$ is small, the approximation for the misclassification in Corollary \ref{coro1} is favorable. This situation occurs very frequently in practice. It can be shown as below.

Note that the mean squared error of estimating $\P(p_1\leq \alpha)=\kappa_1$ is
\begin{align*}
	\E\bigg\{ \Big\{ \sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)-\kappa_1 \Big\}^2 \bigg\}
	&= \Big\{ \sum_{i\in \mc{I}_n} w_i \kappa_i -\kappa_1 \Big\}^2 + \var 
	\Big\{\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha) \Big\}\\
	&= \Big\{ \sum_{i\in \mc{I}_n} w_i \kappa_i -\kappa_1 \Big\}^2  + \sum_{i\in \mc{I}_n} w_i^2 \kappa_i (1-\kappa_i) \\
	& \overset{n\to \infty }{\to} \sum_{i\in \mc{I}_n} w_i^2 \kappa_i (1-\kappa_i) ,
\end{align*}
where the last second step assumes that $\{I(p_i\leq \alpha)\colon i\in \mc{I}_n\}$ are independent and the last step uses the condition $\sum_{i\in \mc{I}_n} w_i \kappa_i \to \kappa_1$ as $n\to \infty$, which is used in Corollary \ref{coro1}. Notice that if $\kappa_i$ is very small, the mean squared error of $\sum_{i\in \mc{I}_n} w_i I(p_i\leq \alpha)$ turns out to be small such that by the rationale of the proof of Proposition \ref{votprop}, the asymptotic approximation for the misclassification error in  Corollary \ref{coro1} should be acceptable.

@@

\section{Numerical Examples}

\begin{table}[H]
	\begin{center}
		\begin{tabular}{cccccc}
  \hline
 & null & Permanent & Decay without scale & Decay with scale & Complicate \\ 
  \hline
TS2 & 239.71 & 241.70 & 241.71 & 242.91 & 236.17 \\ 
  TS3 & 276.52 & 277.73 & 272.63 & 275.79 & 274.25 \\ 
  TS4 & 215.67 & 212.55 & 214.45 & 211.37 & 198.31 \\ 
  Mean & 243.97 & 244.00 & 242.93 & 243.36 & 236.24 \\ 
  TS1 & 262.59 & 260.58 & 239.07 & 266.03 & 206.03 \\ 
   \hline
\end{tabular}
	\end{center}	
\end{table}

\begin{table}
\begin{center}
  \begin{tabular}{cccccccccr}
     $L$ ($T_i-T^*_i$) & Model & $p_1$ & $\mathbf{W}^*=(0,0,1)$ & $|\hat{p}-p_1|$ & Vote & weighted Vote  & weighted  AIC\\
     \hline 
     7 & Permanent & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0} & $212.554$ \\
     7 & Decaying & 0 && $0.395$ &  0 (incorrect)  & 0 (incorrect) & $214.447$ \\
      7 & Complicate & 1 && $0.090$   &  \textcolor{red}{0} & \textcolor{red}{0}  & 198.307 \\[.2cm]
     15 & Permanent & 1 &  & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 249.637 \\
     15 & Decaying & 0 & & 0 & \textcolor{red}{0} & \textcolor{red}{0}   & $250.107$  \\
     15 & Complicate & 1 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  & $232.084$\\[.2cm]
     30 & Permanent & 1 &  & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  302.089 \\
     30 & Decaying & 0 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  &  $302.432$ \\
     30 & Complicate & 1 & & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 298.345
  \end{tabular}
\end{center}	
\end{table}
